Columnar VCF using Zarr

### 2024-03-08 paper.tex
Update whole-matrix-compute figure

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=6cm]{figures/whole-matrix-compute} &
\begin{tcolorbox}[width=7cm]
\begin{minted}[fontsize=\footnotesize]{python}
def sgkit_afdist(ds, num_bins=10):
    ds_vs = sgkit.variant_stats(ds).compute()
    bins = np.linspace(0, 1.0, num_bins + 1)
    bins[-1] += 0.01
    af = ds_vs.variant_allele_frequency.values[:, 1]
    pRA = 2 * af * (1 - af)
    pAA = af * af
    hets = ds_vs.variant_n_het.values
    homs = ds_vs.variant_n_hom_alt.values
    a = np.bincount(
        np.digitize(pRA, bins),
        weights=hets,
        minlength=num_bins + 1)
    b = np.bincount(
        np.digitize(pAA, bins),
        weights=homs,
        minlength=num_bins + 1)
    count = (a + b).astype(int)
    return pd.DataFrame({
        "start": bins[:-1],
        "stop": bins[1:],
        "prob_dist":
        count[1:]})

ds = sgkit.load_dataset(ds_path)
df = sgkit_afdist(ds)
\end{minted}
\end{tcolorbox}
\end{tabular}
\caption{Whole-matrix compute performance with increasing sample size.
(A) Total CPU time required to run \texttt{bcftools +afdist}
and equivalent operations in a single thread for various tools.
Elapsed time is also reported (dotted line).
(B) Relative speedup with 8 threads.
(C) The source code used for the sgkit version of afdist used in these
benchmarks. See Figure~\ref{fig-whole-matrix-compute-supplemental} for
more detailed comparisons with different numbers of threads, and comparing
the effects of HDD vs SSD storage.
\label{fig-whole-matrix-compute}}
\end{figure*}

>>>>

\begin{figure}
\includegraphics[width=6cm]{figures/whole-matrix-compute}
\caption{Whole-matrix compute performance with increasing sample size.
(A) Total CPU time required to run \texttt{bcftools +afdist}
and equivalent operations in a single thread for various tools.
Elapsed time is also reported (dotted line). Run-time for genozip
at $10^6$ samples was extrapolated by fitting an exponential.
\label{fig-whole-matrix-compute}}
\end{figure}
